Figure 1f

### 2017-11-20 inst/cellular_localization/cellular_localization.Rmd
more of the previous commit 2

packages <- c(
    "tidyverse",
    "printr",
    "ggthemes",
    "readr",
    "miR34AasRNAproject",
    "grid",
    "gtable"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

@@

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst/"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

@@

figure <- plotPDF(p)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure1e_cellularLocalization/suppFigure1e_cellularLocalization.pdf"

>>>>

packages <- c(
  "tidyverse",
  "printr",
  "ggthemes",
  "readr",
  "miR34AasRNAproject",
  "grid",
  "gtable",
  "grDevices"
)
purrr::walk(packages, library, character.only = TRUE)
rm(packages)

@@

projectUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/inst"
dataUrl <- "https://github.com/GranderLab/miR34a_asRNA_project/raw/master/"

@@

figure <- plotPDF(p)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1e"][[1]])

### 2017-11-20 inst/coding_potential_cpat/coding_potential_cpat.Rmd
more of the previous commit 2

url <- "figure1f_codingPotentialCPAT/results.txt"
cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
cpat

>>>>

#url <- "figure1f_codingPotentialCPAT/results.txt"
url <- fileMap(type = "png")["figure1f"][[1]]

cpat <-read.table(url(file.path(projectUrl, url)), header = TRUE, sep = "\t")
cpat
